Rapid cycleway prioritisation tool

### 2020-06-03 code/index.Rmd
Update layer descriptions

## 1. Key cycle routes

This layer is designed to represent a cohesive network of direct routes.
It shows what a joined-up cycle network could look like if there were no constraints on road space, along some of the most important corridors.
The layer takes no account spare space and is designed to support consideratioin of alternative options, e.g. one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The layer was developed based on evidence on the importance of active transport network that are continuous and do not 'give up' at awkward junctions.
The layer was created by selecting all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads.
These segments are then joined together to form a continuous network.

>>>>

## 1. Cohesive network

This layer is designed to represent a cohesive network of direct routes.
It shows what a joined-up cycle network could look like if there were no constraints on road space, along some of the most important corridors.

The layer takes no account spare space and is designed to support consideratioin of alternative options, e.g. one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The cohesive network layer was created based on evidence that cohesive cycle networks, that are continuous and do not 'give up' at awkward junctions, are a key component of plans to get people cycling.

The layer was generated by first identifying the roads (classified by reference number) on which there is most cycling potential accross the city and joining them together.
Specifically we first selected all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads.
These segments are then joined together to form a continuous network.
